\documentclass{kththesis}

\usepackage{blindtext} % This is just to get some nonsense text in this template, can be safely removed

\usepackage{csquotes} % Recommended by biblatex
\usepackage{biblatex}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumerate}
\usepackage{gensymb}
\usepackage{multirow}
\usepackage{float}
\usepackage{amsmath,amssymb}
\usepackage{listings}

\DeclareRobustCommand{\bbone}{\text{\usefont{U}{bbold}{m}{n}1}}

\DeclareMathOperator{\EX}{\mathbb{E}}
\DeclareMathOperator{\Lagr}{\mathcal{L}}

\addbibresource{ex.bib} % The file containing our references, in BibTeX format


\title{This is the English title}
\alttitle{Detta är den svenska översättningen av titeln}
\author{Osquar Student}
\email{osquar@kth.se}
\supervisor{Lotta Larsson}
\examiner{Lennart Bladgren}
\programme{Master in Computer Science}
\school{School of Electrical Engineering and Computer Science}
\date{\today}


\begin{document}
\section{Comparison with earlier work}
\begin{center}
\captionof*{table}{Comparison on the ISPRS Potsdam dataset} \label{tab:potsdam} 
\begin{tabular}{|c | c | c|}
\hline
\textbf{Model} & Proposed Model & SBD \\
\textbf{Resolution used} & \textbf{30 cm/pixel} & 12.5 cm/pixel\\
\textbf{Pixelwise F1 score} & 0.851 & \textbf{0.884}\\
\textbf{Vehiclewise F1 score} & \textbf{0.800} &  0.773\\
\textbf{Mean prediction error counting cars} & \textbf{1.67 \%} &  3.57 \%\\
\textbf{Evaluation time per tile*} & \textbf{0.19 seconds} &  28.19 seconds\\
\hline
\end{tabular}\caption{Shows the comparison between the proposed model and the Segment before you Detect (SBD) model \parencite{audebert_usability_2016} on the Potsdam dataset.\\ \textbf{*} The SBD model was evaluated on a Tesla K20 which can at maximum perform $3.52*10^{12}$ 32 bit floating point operations per second. The proposed model was evaluated on a Tesla K80 wich can perform at maximum $8.74*10^{12}$ 32 bit floating point operations per second. Therefore the evaluation time on the SBD model was multiplied with $3.52/8.74\approx0.4027$ to make fair comparisons. The evaluation time should therefore not be regarded as exact but as an indication of the speed difference between the two models.}
\end{center}

\begin{center}
\captionof*{table}{Comparison on the Vedai dataset} \label{tab:vedai} 
\begin{tabular}{|c | c c|}
\hline
\textbf{Model} & \textbf{Detection time per image*}  & \textbf{Vehiclewise F1 score}\\
\hline
Faster R-CNN (Z\&F) & 0.1998 & 0.212\\
Faster R-CNN (VGG-16) & 0.2248 & 0.225\\
Fast R-CNN (VGG-16) & 3.1465 &  0.224\\
CCNN &0.2736 &  0.305\\
Proposed Model & $\approx$ \textbf{0.19/4} & \textbf{0.554}\\
\hline
\end{tabular}
\caption{Shows the comparison between the proposed model and the Faster R-CNN (Z\&F), Faster R-CNN (VGG-16), Fast R-CNN (VGG-16) \parencite{zeiler_visualizing_2014} and the Cascaded Convolutional Neural Networks (CCNN) \parencite{zhong_robust_2017-1} on the Vedai dataset. \textbf{*} The other models were evaluated on a Titan X which can at maximum perform $11*10^{12}$ 32 bit floating point operations per second. The proposed model was evaluated on a Tesla K80 wich can perform at maximum $8.74*10^{12}$ 32 bit floating point operations per second. Therefore the evaluation time on the compared models were multiplied with $11/8.74\approx1.2586$ to make fair comparisons. The evaluation time should therefore not be regarded as exact but as an indication of the speed difference between the two models.}
\end{center}
%Potsdam/bin_labels_resized/top_potsdam_2_11_RGB.tif
%2018-04-17 08:47:13,406 time: 2.2504019737243652
%107
%108
%107
%[107, 83, 25, 24, 0.7685185185185185, 0.7757009345794392, 0.7720930232558139]
%Potsdam/bin_labels_resized/top_potsdam_7_12_RGB.tif
%2018-04-17 08:47:25,775 time: 0.16370177268981934
%346
%347
%346
%[346, 278, 59, 68, 0.8249258160237388, 0.8034682080924855, 0.8140556368960469]
%Potsdam/bin_labels_resized/top_potsdam_7_11_RGB.tif
%2018-04-17 08:47:38,697 time: 0.15589356422424316
%346
%347
%346
%[346, 291, 61, 55, 0.8267045454545454, 0.8410404624277457, 0.833810888252149]
%Potsdam/bin_labels_resized/top_potsdam_7_10_RGB.tif
%2018-04-17 08:47:51,576 time: 0.2106609344482422
%250
%251
%250
%[250, 203, 48, 47, 0.8087649402390438, 0.812, 0.810379241516966]
%Potsdam/bin_labels_resized/top_potsdam_7_9_RGB.tif
%2018-04-17 08:48:04,344 time: 0.18450117111206055
%304
%305
%304
%[304, 230, 80, 74, 0.7419354838709677, 0.756578947368421, 0.749185667752443]
%Potsdam/bin_labels_resized/top_potsdam_2_12_RGB.tif
%2018-04-17 08:48:17,134 time: 0.17915034294128418
%123
%124
%123
%[123, 100, 26, 23, 0.7936507936507936, 0.8130081300813008, 0.8032128514056225]
%[246.0, 197.5, 49.833333333333336, 48.5, 0.794083349626268, 0.8002994470915654]

\printbibliography[heading=bibintoc] % Print the bibliography (and make it appear in the table of contents)
\end{document}
